The Galactic Delay-Time Distribution of Type Ia Supernovae:\\ A Chemical Evolution Perspective

### 2023-07-27 src/tex/ms.tex
[showyourwork] overleaf sync

\begin{figure}
    \centering
    \includegraphics{figures/age_ofe_sfh.pdf}
    \caption{A comparison of the age--[O/Fe] relation between multi-zone simulations with different SFH models. All assume an inside-out SFH. Each row contains star particles from a different bin in $|z|$, with stars closest to the midplane in the bottom row and stars farthest from the midplane in the top row. Each panel plots a random mass-weighted sample of 10,000 star particles in the Solar annulus ($7\leq R_{\rm gal}<9$ kpc) color-coded by the Galactocentric radius at birth. A Gaussian scatter has been applied to all points based on the median [O/Fe] error from APOGEE DR17 and the median age error from \citet{Leung2023-Ages}. Black squares represent the mass-weighted median age of star particles within bins of [O/Fe] with a width of 0.05 dex, and the horizontal black error bars encompass the 16th and 84th percentiles. Red triangles represent the median age from \citet{Leung2023-Ages} in bins of [O/Fe], and the horizontal red error bars encompass the 16th and 84th percentiles. For clarity, bins which contain less than 1\% of the total mass (in the simulations) or total number of stars (in the data) are not plotted. Similar to Figure \ref{fig:age-ofe-dtd} but for simulations with different SFH models. All assume an exponential DTD with $\tau=1.5$ Gyr. In all panels, stars are limited to the Solar neighborhood ($7\leq R_{\rm gal}<9$ kpc, $0\leq|z|<0.5$ kpc)}
    \label{fig:age-ofe-sfh}
    \script{age_ofe_sfh.py}
\end{figure}

\begin{figure*}
    \centering
    \includegraphics{figures/age_ofe_dtd.pdf}
    \caption{A comparison of the age--[O/Fe] relation between multi-zone simulations with different DTD models. All assume an inside-out SFH. Each row contains star particles from a different bin in $|z|$, with stars closest to the midplane in the bottom row and stars farthest from the midplane in the top row. Each panel plots a random mass-weighted sample of 10,000 star particles in the Solar annulus ($7\leq R_{\rm gal}<9$ kpc) color-coded by the Galactocentric radius at birth. A Gaussian scatter has been applied to all points based on the median [O/Fe] error from APOGEE DR17 and the median age error from \citet{Leung2023-Ages}. Black squares represent the mass-weighted median age of star particles within bins of [O/Fe] with a width of 0.05 dex, and the horizontal black error bars encompass the 16th and 84th percentiles. Red triangles represent the median age from \citet{Leung2023-Ages} in bins of [O/Fe], and the horizontal red error bars encompass the 16th and 84th percentiles. For clarity, bins which contain less than 1\% of the total mass (in the simulations) or total number of stars (in the data) are not plotted.}
    \label{fig:age-ofe-dtd}
    \script{age_ofe_dtd.py}
\end{figure*}

@@

\begin{figure*}
    \centering
    \includegraphics{figures/dtd_analytical.pdf}
    \includegraphics{figures/onezone_analytical_dtd.pdf}
    \caption{\textit{Left:} Analytical DTDs from \citet[][solid curves]{Greggio2005-AnalyticalRates} and simple DTD functions (dashed curves). Some functions are presented with a constant multiplicative factor for visual clarity. \textit{Right:} Abundance tracks and distributions from one-zone models with the analytical and simple DTDs (same color scheme). For clarity, we vary the mass-loading factor to be $\eta=4$, $\eta=2$, and $\eta=1$ for the red, green, and blue curves, respectively.}
    \label{fig:analytical-dtd}
    \script{analytical_dtd_twopanel.py}
\end{figure*}

>>>>

\begin{figure}
    \centering
    \includegraphics{figures/age_ofe_sfh.pdf}
    \caption{A comparison of the age--[O/Fe] relation between multi-zone simulations with different SFH models. All assume an exponential DTD with $\tau=1.5$ Gyr. Each panel plots a random mass-weighted sample of 10,000 star particles in the Solar neighborhood ($7\leq R_{\rm gal}<9$ kpc, $0\leq|z|<0.5$ kpc) color-coded by the Galactocentric radius at birth. A Gaussian scatter has been applied to all points based on the median [O/Fe] error from APOGEE DR17 and the median age error from \citet{Leung2023-Ages} (see Table \ref{tab:uncertainties}). Black squares represent the mass-weighted median age of star particles within bins of [O/Fe] with a width of 0.05 dex, and the horizontal black error bars encompass the 16th and 84th percentiles. Red triangles represent the median age from \citet{Leung2023-Ages} in bins of [O/Fe], and the horizontal red error bars encompass the 16th and 84th percentiles. For clarity, bins which contain less than 1\% of the total mass (in the simulations) or total number of stars (in the data) are not plotted.}
    \label{fig:age-ofe-sfh}
    \script{age_ofe_sfh.py}
\end{figure}

\begin{figure*}
    \centering
    \includegraphics{figures/age_ofe_dtd.pdf}
    \caption{A comparison of the age--[O/Fe] relation between multi-zone simulations with different DTD models. All assume an inside-out SFH. Each row contains star particles from a different bin in $|z|$, with stars closest to the midplane in the bottom row and stars farthest from the midplane in the top row. In all panels stars are limited to the Solar annulus ($7\leq R_{\rm gal}<9$ kpc), and the layout of each panel is as in Figure \ref{fig:age-ofe-sfh}.}
    \label{fig:age-ofe-dtd}
    \script{age_ofe_dtd.py}
\end{figure*}

@@

\begin{figure*}
    \centering
    \includegraphics{figures/dtd_analytical.pdf}
    \includegraphics{figures/onezone_analytical_dtd.pdf}
    \caption{\textit{Left:} Analytical DTDs from \citet[][solid curves]{Greggio2005-AnalyticalRates} and simple DTD functions (dashed curves). Some functions are presented with a constant multiplicative factor for visual clarity. \textit{Right:} Abundance tracks and distributions from one-zone models with the analytical and simple DTDs (same color scheme). For clarity, we vary the mass-loading factor to be $\eta=4$, $\eta=2$, and $\eta=1$ for the red, green, and blue curves, respectively. All simulation parameters between the similarly-colored solid and dashed curves are identical.}
    \label{fig:analytical-dtd}
    \script{analytical_dtd_twopanel.py}
\end{figure*}
